Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2021-11-14 bbbq_article.tex
Updates from Overleaf

\frans{This section requires review}
\richel{This section requires review indeed}

From the IEDB,
we obtained \richel{53,041}
and \richel{2,495} linear epitope sequences for our MHC-I 
and MHC-II alleles respectively.
There are relatively few epitopes for MHC-II, 
as MHC-II has many more different alleles than MHC-I \richel{describe how an
MHC-II allele is a combation of two alleles}, 
where we select only the 21 MHC-II alleles used in this study.

Figure \ref{fig:2a} shows that there is a correlation between the
percentage of TMH-derived epitopes that is presented \emph{in vivo}
versus the percentage of TMH-derived epitopes that is predicted to be presented
in MHC-I alleles. For MHC-II alleles, there were too few epitopes per MHC allele
to result in an informative figure.

We grouped all epitopes presented by MHC-I and MHC-II alleles and show 
the percentage of which these were TMH-derived in figure \ref{fig:2c}.
\richel{value}\% and \richel{value}\% were
predicted to be TMH-derived epitopes.
\richel{Indeed, what is the null hypothesis? The original one is that
zero percent of all TMH derived epitopes is presented, rendering statistics
useless. However, what about testing if TMH-derived epitopes are presented
just as often as TMHs are part of the proteom?}.

@@

%
% Figure 2
%
\begin{figure}[!htbp]
  \centering
  \begin{subfigure}[t]{0.45\textwidth}
    \centering
    \caption{}
    \includegraphics[width=1.0\textwidth]{bbbq_article_issue_157/figure_2a.png}
    \label{fig:2a}
  \end{subfigure}  
  \hfill
  \begin{subfigure}[t]{0.45\textwidth}
    \centering
    \caption{}
    \includegraphics[width=1.0\textwidth]{bbbq_article_issue_157/figure_2c.png}
    \label{fig:2c}
  \end{subfigure}

@@

@@

\begin{figure}[!htbp]
  \centering
  \includegraphics[width=0.5\textwidth]{bbbq_article_issue_157/figure_2d.png}
  \caption{
    \textbf{
      T cells present TMH-derived epitopes \emph{in vivo}
    }
    The numbers above the bars denotes the number of epitopes
    found in the IEDB for the MHC alleles used in this study
    \richel{Numbers must be approx 259 and 651}
  }
  \label{fig:t_cells_present_tmh_derived_epitopes}
\end{figure}

>>>>

The IEDB contains millions of linear epitope sequences obtained
by an MHC ligand assay.
For the MHC alleles used in this study, 
we obtained 54,303 and 2,484 linear epitope sequences for the MHC-I
and MHC-II alleles respectively.
There are relatively few epitopes for MHC-II, 
as MHC-II has many more different alleles than MHC-I, 
where we select only the 21 MHC-II alleles used in this study.

Figure \ref{fig:2a} shows that there are similar levels of
over-presentation of TMH-derived epitopes between (1) the
percentage of TMH-derived epitopes that is presented \emph{in vivo}
versus (2) the percentage of TMH-derived epitopes that is predicted to be presented
in MHC-I alleles. For MHC-II alleles, there were too few epitopes per MHC allele
to result in an informative figure.

We grouped all epitopes presented by MHC-I and MHC-II alleles and show 
the percentage of which these were TMH-derived in figure \ref{fig:2b}.
\richel{value}\% and \richel{value}\% were
predicted to be TMH-derived epitopes.
\richel{Indeed, what is the null hypothesis? The original one is that
zero percent of all TMH derived epitopes is presented, rendering statistics
useless. However, what about testing if TMH-derived epitopes are presented
just as often as TMHs are part of the proteom?}.

@@

%
% Figure 2
%
\begin{figure}[!htbp]
  \centering
  \begin{subfigure}[t]{0.45\textwidth}
    \centering
    \caption{}
    \includegraphics[width=1.0\textwidth]{bbbq_article_issue_157/figure_2a.png}
    \label{fig:2a}
  \end{subfigure}  
  \hfill
  \begin{subfigure}[t]{0.45\textwidth}
    \centering
    \caption{}
    \includegraphics[width=1.0\textwidth]{bbbq_article_issue_157/figure_2b.png}
    \label{fig:2b}
  \end{subfigure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Correlation of epitope presentation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In the main text of this research, we use two sources of epitopes
to determine if TMH-derived epitopes are presented.
The first source of epitopes are all the 9-mers (for MHC-I) (and 15-mers for MHC-II)
derived from a human reference proteome, where this over-presentation
is displayed in figure \ref{fig:bbbq_1_smart_results}.
The second source of epitopes are those that are present in the IEDB
that are obtained from MHC ligand assays,
as displayed in figure \ref{fig:2a}.

Here we correlate between the over-presentation of TMH-derived
epitopes between these two sources of data.
Figure \ref{fig:thm_presentation_correlation} shows per haplotype
the percentage of TMH-derived epitopes, with a linear trendline.

\begin{figure}[!htbp]
  \centering
  \includegraphics[width=0.5\textwidth]{bbbq_article_issue_157/figure_2c.png}
  \caption{
    \textbf{
      TMH-derived epitopes are over-presented when using
      predicted as well as \emph{in vivo} data
    }
    For the MHC class I alleles, the over-presentation of
    TMH-derived epitopes is correlated between 
    IEDB MHC ligand epitopes (horizontal axis) and the 9-mers
    derived from a human reference proteome (vertical axis).
    The trendline shows the linear correlation between these
    percentages, where the gray area is the 95\% confidence interval.
  }
  \label{fig:thm_presentation_correlation}
\end{figure}

@@

\begin{figure}[!htbp]
  \centering
  \includegraphics[width=0.5\textwidth]{bbbq_article_issue_157/figure_2d.png}
  \caption{
    \textbf{
      T cells present TMH-derived epitopes \emph{in vivo}
    }
    The numbers above the bars denotes the number of epitopes
    found in the IEDB for the MHC alleles used in this study.
  }
  \label{fig:t_cells_present_tmh_derived_epitopes}
\end{figure}
